|

### 2019-07-30 article/article.Rmd
small fixes

# Introduction\label{sec:intro}

One of the key determinants of efficient public service provision is a robust accountability system \citep{besley2003incentives,cameron2004public,o1998horizontal}. In its standard definition, accountability is the process of holding authorities into account for their actions \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}. Recent studies show that accountability ensures that politicians act on behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the opportunities for rent-seeking and corruption \citep{deininger2005does,wenar2006accountability} and increases the efficiency of the public sector \citep{adsera2003you,bjorkman2009power}. Moreover, greater accountability is associated with higher levels of economic growth, not only because it limits state discretion in the economy, but also because it promotes social cohesion and long-term investments in human capital \citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.

However, accountability systems can take many forms. One promising model for democratic oversight is _bottom-up accountability_, in which citizens receive information about the shortcomings of a given project to help them monitor and pressure underperforming public officials \citep{kosack2014does, molina2016community,raffler2018weakness}. Proponents suggest bottom-up is an effective method of accountability because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities \citep[570]{serra2011combining}. In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve \citep[2]{raffler2018weakness}.

@@

# The _Tá de Pé_ App

# Methods

## Estimation

@@

# Results

# Discussion

# Conclusion

>>>>

# Introduction
\label{sec:intro}

One of the key determinants of efficient public service provision is a robust accountability system \citep{besley2003incentives,cameron2004public,o1998horizontal}. In its standard definition, accountability is the process of holding authorities into account for their actions \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}. Past studies show that accountability ensures that politicians act on behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the opportunities for rent-seeking and corruption \citep{deininger2005does,wenar2006accountability} and increases the efficiency of the public sector \citep{adsera2003you,bjorkman2009power}. Moreover, greater accountability is associated with higher levels of economic growth, not only because it limits state discretion in the economy, but also because it promotes social cohesion and long-term investments in human capital \citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.

However, accountability systems can take many forms. One promising model for democratic oversight is _bottom-up accountability_, in which citizens receive information about the shortcomings of a given project to help them monitor and pressure underperforming public officials \citep{kosack2014does, molina2016community,raffler2018weakness}. Proponents suggest bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities \citep[570]{serra2011combining}. In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve \citep[2]{raffler2018weakness}.

@@

# The _Tá de Pé_ App
\label{sec:tdp}

# Methods
\label{sec:methods}

## Estimation
\label{sub:estimation}

@@

# Results
\label{sec:results}

# Discussion
\label{sec:discussion}

# Conclusion
\label{sec:conclusion}
